Individual heterogeneity in functional topography of the default-mode network in medial prefrontal cortex

### 2019-04-18 Manuscript.Rmd
renamed variables, and deleted unnecessary ones from data, manuscript, and graphAnalysis script

``` {r Load Summary Data}
# Load data
setwd('./Summary/')
temp <- list.files()
subjList <- sapply(temp, substring, first = 1, last = 6)
Summaries <- lapply(temp, read.csv)
nSubj <- length(Summaries)
nVertices <- nrow(Summaries[[1]]) # in case I need the number of vertices included per brain
```

@@

### Testing grounds
# this part compares the distribution of Fiedler values for DMN and nonDMN
# note: remove filter(y > 0) for 'full brain'
# First plot compares the median FV between communities across subjects
allSummaries <- do.call(rbind, Summaries)
allSummaries$SubjID <- rep(subjList, each = nVertices) 
ecdfPCC <- allSummaries %>%
          mutate(FV_abs = abs(FiedlerVec),
                 Community = ifelse(FiedlerBinary == 0, "nonDMN", "DMN")) %>%
          filter(y < 0) %>%
          ggplot(aes(FV_abs, group = interaction(SubjID, Community), color = Community)) +
          stat_ecdf(alpha = 0.3) +
          #scale_color_manual(values = c("Yellow", "Red")) +
          xlim(0,0.05) +
          geom_vline(xintercept = 0.009, lty = 2) +
          labs(title = "Per-subject ECDF of Fiedler values: PCC") +
          theme_classic()

ecdfPFC <- allSummaries %>%
          mutate(FV_abs = abs(FiedlerVec),
                 Community = ifelse(FiedlerBinary == 0, "nonDMN", "DMN")) %>%
          filter(y > 0) %>%
          ggplot(aes(FV_abs, group = interaction(SubjID, Community), color = Community)) +
          #scale_color_manual(values = c("Yellow", "Red")) +
          stat_ecdf(alpha = 0.3) +
          xlim(0,0.05) +
          labs(title = "Per-subject ECDF of Fiedler values: PFC") +
          geom_vline(xintercept = 0.009, lty = 2) +
          theme_classic()

ecdfALL <- allSummaries %>%
  mutate(FV_abs = abs(FiedlerVec),
         Community = ifelse(FiedlerBinary == 0, "nonDMN", "DMN")) %>%
  ggplot(aes(FV_abs, group = interaction(SubjID, Community), color = Community)) +
  #scale_color_manual(values = c("Yellow", "Red")) +
  stat_ecdf(alpha = 0.5) +
  xlim(0,0.05) +
  labs(title = "Per-subject ECDF of Fiedler values") +
  geom_vline(xintercept = 0.009, lty = 2) +
  theme_classic()

@@

@@

Foo <- "fighters"
```

>>>>

``` {r Load Summary Data}
# Load data
setwd('./Summary/')
temp <- list.files()
subjList <- sapply(temp, substring, first = 1, last = 6)
Summaries <- lapply(temp, read.csv)
nSubj <- length(Summaries)
nVertices <- nrow(Summaries[[1]]) # in case I need the number of vertices included per brain

@@

@@

# put all summaries together for model fit
allSummaries <- do.call(rbind, Summaries)
allSummaries$SubjID <- rep(subjList, each = nVertices)

@@
